### 2024-01-09 doc/Thesis/chapter/050-results-material.tex
change lambda to n_L

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of the Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, there was no improvement and the results examined with \td{\gls{sem} (where is the evidence?)} reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.79\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.8\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of of \gls{zro}:
		(a) \gls{zro} produces by aquatic solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
These - I think - are rather only one layer deep irregularities since they are so prevalent
and hardly any pin holes were electrically observed on similar samples. 
\todo{where is the evidence?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow), \gls{zro} (blue), $\alpha$-Fe (green, idealized) and cubic-\gls{zro} (purple, idealized)\cite{gkatz1971xray} \td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Material Properties of the Produced Layers}
\label{sec:res-mat}
%\todo{of what?}
%\subsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.~\cite{Anwar2017} failed to produce a homogeneous layer of \gls{zro}.
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure~\ref{fig:sem-old}). 
Altering the ratio of ingredients, adjusting pH (by adding \gls{naoh}, \gls{h2so4} or \gls{hcl}) or adding \gls{sds} as surfactant did not increase the resistance of the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers, 
there was no significant improvement and the results examined with \gls{sem} (see figure~\ref{fig:sem-old}) reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure~\ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure~\ref{fig:sem-old1}) and double (figure~\ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non-coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

\begin{figure}[bht]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.79\textwidth]{Pics/sem/071_fto_old_1x1F.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/071_fto_old_2x.png}
		\caption{}%SEM picture of \gls{zro} produces by H2O solution} 
		\label{fig:sem-old}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/147_steel_ph_10x.png}
		\caption{}%SEM picture of \gls{zro} produced by buoh solution} 
		\label{fig:sem-ph}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/sem/115_fto_cs_1x.png}
		\caption{}%115 fto cs 5x} 
		\label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        %\includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \includegraphics[width=.99\textwidth]{Pics/sem/150_steel_cs_2Fx5.png}
		\caption{}%150 steel 2Fx5} 
		\label{fig:sem-cs2}
    \end{subfigure}
	\caption{
		SEM images of of \gls{zro}:
		(a) \gls{zro} produces by 2 layers aquatic solution on \gls{fto}
		(b) 10 layers of \gls{zro} on steel substrate
		(c) cross section of crack of 5 layers of \gls{zro} on \gls{fto}
		(d) side view of scratched \gls{zro} on steel substrate
		%SEM images of \gls{zro} on top of \gls{fto} (a,c) and \gls{zro} on steel (b,d) \td{find bu sol on fto and show only steel}} 
		\label{fig:sem}
	}
\end{figure}
\enlargethispage{-\baselineskip}

The sol-gel recipe optimized by Hu et al.\cite{Hu2016} for \ch{Al2O3} worked splendidly for our use case even after (not so) minor changes (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a (tiny) hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible slits spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}
